---
title: "Using the package"
author: "Aditya Sharma"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)

library(FirstRPackage)
```

This package helps users to read the files in the directory and summarise number of accidents by month and year. The package contains the functions fars_read(), make_filename(), fars_read_years(), fars_summarize_years() and fars_map_state().

We'll be explaining each function with examples.

### fars_read()

This is a simple function that reads a file by taking filename as input. If a filename doesn't exist in the working directory then the function stops with the message "file 'filename' does not exist".

```{r}
fars_read('accident_2013.csv.bz2')

```

### make_filename()

This is a simple function that creates a filename in the ".csv.bz2" format starting with "accident_" for a given year.

```{r}
make_filename(2018)
```

### fars_read_years()

This function let's us read multiple files by just inputting the years for which we want to read files. It generates a list of data frames, where each file is a data frame that's part of the list.

```{r}
fars_read_years(c(2013, 2014, 2015))
```

### fars_summarize_years()

This function calculates a summary of total accidents by month and year.

```{r}
fars_summarize_years(c(2013, 2014, 2015))
```

### fars_map_state()

This function let's us show accidents by exact location in a state within a year on a map. If there are no accidents for a state in a year, then a message "no accidents to plot" would vbe shown. The "state.num" should be valid otherwise the function would stop and show the message "invalid STATE number: 'state.num'".

```{r}
fars_map_state(24, 2013)
```

